### 2025-02-08 short/sections/training.tex
Create training.tex

\cvsection{Relevant Research Projects}

@@

\begin{cvhonors}
\cvhonor
{Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
{NWO VIDI SWG Project VI.Vidi.211.226, {\bfseries PostDoc} (Natascha van der Zwan, PI), about USD\$1 000 000. Period: 2024-2026.} %% {\pounds} 800 000
{Dutch Research Agency}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), {\bfseries PI}, about USD\$2 000. Period: 2024-2025.} %% {\pounds} 1 500
{UDP}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
{OpenAI Academic Programme, {\bfseries PI}, about USD\$5 000. Period: 2024.}
{OpenAI}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Unravelling the Rule of Law: A Machine Learning Approach}
{NWO XS Project 406.XS.01.013, {\bfseries PostDoc} (Jaroslaw Kantorowicz, PI), about USD\$60 000. Period: 2023-2024.} %% {\pounds} 45 000
{Dutch Research Agency}
{2023}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), {\bfseries PI}, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
{USACH}
{2022}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), {\bfseries Research Associate} (Ximena Orchard, PI), about USD\$4 000. Period: 2019.} %% {\pounds} 3 000
{UAH}
{2019}
\end{cvhonors}

>>>>

\cvsection{Relevant Certification \& Training}

@@

\begin{cvhonors}
\cvhonor
{KODAQS Data Quality Academy Certificate Program, University of Mannheim} 
{Data quality dimensions, indicators and metrics to assess data quality, tools and data quality, data management procedures, reproducibility} 
{Mannheim, DEU}
{2025}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ODISSEI Summer Institute in Computational Social Science} 
{Network analysis, machine learning, benchmarking and ethics} 
{Rotterdam, NLD}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Introduction to Learning and Teaching at Oxford} 
{Foundations for inclusive teaching and strategies to support efficient and effective preparation for teaching} 
{Oxford, GBR}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Oxford|Berlin Summer School on Open Research} 
{Training in biases in research, reproducibility, publishing, open data, open materials, meta-research and ethical conduct of research} 
{Oxford, GBR}
{2021}
\end{cvhonors}

\vspace{1mm}
%% \pagebreak
